Appendix

### 2020-11-17 manuscript/article.tex
text

\noindent In a seminal article, \citet{weingast1981political} argue that there
is a positive relationship between legislature size and inefficiency in public
expenditures. Their proposition is currently known as the ``law of $1/n$'' and
has been widely debated in political science and public administration.
However, recent studies have questioned the validity of the theory. In this
letter, we estimate the first meta-analysis of the relationship between the
number of legislators and public spending. Based on a sample of \textbf{XX}
articles, we find only mixed evidence for the effect of legislature size on
government budgets. Yet the aggregate results mask important differences. While
earlier, non-causal studies provide moderate support for the ``law of $1/n$'',
recent papers using causal inference methods consistently find a negative
relation between seats and spending, suggesting that previous results might
have been driven by spurious correlations or omitted variable bias. The
available evidence also indicates that XXXXXXXXXXXXXXXX

@@

In this letter, we conduct the first meta-analysis that tests the generality of
the ``law of $1/n$''. We have selected 26 articles that use quantitative methods
to analyse the impact of legislature size over government spending. We run two
sets of models: the first group uses only the main estimates of each paper (36),
while the second set includes all coefficients reported in our sample
(126).\footnote{Although there are 26 papers in our review, we include 36
coefficients in the restricted sample. This is because 10 articles report
separate estimates for the impact of lower and upper house size on government
expenditures. In the full model, we add every outcome reported in the
papers, regardless of whether the coefficient comes from the main tables or
from robustness checks conducted by the original authors. We discuss our
sampling process in the Methods section of this paper and in the Supplementary
Material.} Our independent variables consist of three measures, namely the size
of the lower chamber ($n$), its natural logarithm (log($n$)), and the number of
members in the upper chamber ($k$). We evaluate their effect upon public
expenditure per capita, the natural logarithm of public expenditure per capita,
and government expenditure as a percentage of GDP. We then estimate if the
results vary according to four potential sources of effect heterogeneity.

>>>>

\noindent In a seminal article, \citet{weingast1981political} argue that there
is a positive relationship between legislature size and inefficiency in public
expenditures. Their proposition is currently known as the ``law of $1/n$'' and
has been widely debated in political science and public administration.
However, recent studies have questioned the validity of the theory. In this
letter, we estimate the first meta-analysis of the relationship between the
number of legislators and public spending. Based on a sample of \textbf{29}
articles, we find only mixed evidence for the effect of legislature size on
government budgets. Yet the aggregate results mask important differences. While
earlier, non-causal studies provide moderate support for the ``law of $1/n$'',
recent papers using causal inference methods consistently find a negative
relation between seats and spending, suggesting that previous results might
have been driven by spurious correlations or omitted variable bias. The
available evidence also indicates that XXXXXXXXXXXXXXXX

@@

In this letter, we conduct the first meta-analysis that tests the generality of
the ``law of $1/n$''. We have selected 29 articles that use quantitative methods
to analyse the impact of legislature size over government spending. We run two
sets of models: the first group uses only the main estimates of each paper (42),
while the second set includes all coefficients reported in our sample
(142).\footnote{Although there are 29 papers in our review, we include 42
coefficients in the restricted sample. This is because 13 articles report
separate estimates for the impact of lower and upper house size on government
expenditures. In the full model, we add every outcome reported in the
papers, regardless of whether the coefficient comes from the main tables or
from robustness checks conducted by the original authors. We discuss our
sampling process in the Methods section of this paper and in the Supplementary
Material.} Our independent variables consist of three measures, namely the size
of the lower chamber ($n$), its natural logarithm (log($n$)), and the number of
members in the upper chamber ($k$). We evaluate their effect upon public
expenditure per capita, the natural logarithm of public expenditure per capita,
and government expenditure as a percentage of GDP. We then estimate if the
results vary according to four potential sources of effect heterogeneity.
